\textmd{\hmwkClass:\ \hmwkTitle}\\ \small{Due\ on\ \hmwkDueDate}

### 2017-05-18 paper/main.tex
intro

\title{
    \textmd{\hmwkClass:\ \hmwkTitle}\\
    % \normalsize{\hmwkClassInstructor}\\
    % \small{Issued\ on\ \hmwkIssueDate}\\
    \small{Due\ on\ \hmwkDueDate}
}
\author{\hmwkAuthorName}
\date{}
\begin{document}
\maketitle
% \section{Introduction}

@@

\section{Infrastructure}
We used the object system from pset 4 to model physical objects in our simulated world, as well as the world itself. Having the ability to create a hierarchy of types allows us to derive new types of physical objects to be simulated from previously defined types (see section Object Types).

>>>>

\title{
    \textmd{\hmwkClass:\ \hmwkTitle}\\
    % \normalsize{\hmwkClassInstructor}\\
    % \small{Issued\ on\ \hmwkIssueDate}\\
    \small{Due\ on\ \hmwkDueDate}
}
\author{\hmwkAuthorName}
\date{}
\begin{document}
\maketitle
\section{Introduction}

Physics can be viewed as the programming language of the natural world. From
quantum mechanics to Newtonian mechanics to relativistic mechanics, the
theories at these different levels of explanation each describe their
primitives, means of combination, and means of abstraction over objects,
relations, and events. Physical particles, objects, and entities are data, and
the laws that govern how they evolve over time are procedures that operate on
this data.

Our project aims to explore this view by implementing a simple physics engine
in scheme. We designed the physics engine to be generic and extensible. For
example, it is very straightforward to define new worlds on the underlying
substrate as well as to define new objects and forces within a given world.
This paper presents the design of the infrastructure for the physics engine,
describes how objects and forces can be easily defined and added on top of the
infrastucture, and illustrate several demonstrations of the system on worlds
with gravitational and electrostatic forces

@@

\section{Infrastructure}

We used the object system from pset 4 to model physical objects in our
simulated world, as well as the world itself. Having the ability to create a
hierarchy of types allows us to derive new types of physical objects to be
simulated from previously defined types (see section Object Types).
